### 2025-08-20 chapters/benchmark.tex
added random forest generation regression plot

As shown in Figure~\ref{fig:anova-kruskal}, none of the $p$-values from either ANOVA or Kruskal–Wallis testing fell below the $\alpha = 0.05$ significance threshold. This result indicates a lack of statistically significant performance variation across hardware scaling steps for all workloads tested, regardless of execution context. The regression coefficients in subfigure~(b) further reinforce this interpretation: the slopes for both core and memory scaling are near zero in most cases, with low \( R^2 \) values suggesting weak or no explanatory power.

>>>>

As shown in Figure~\ref{fig:anova-kruskal}, none of the $p$-values from either ANOVA or Kruskal--Wallis testing fell below the $\alpha = 0.05$ significance threshold. This indicates a lack of statistically significant performance variation across hardware scaling steps for all workloads tested. The $R^2$ values in subfigure~\ref{fig:r2_grouped} support this, with low model fit observed in both linear and Random Forest regressions, suggesting weak or no explanatory power.
